---
title: "R Notebook"
output: html_notebook
---

```{r}
library(sf)
library(dplyr)
library(readr)
library(stringr)
```

```{r}
sentinel <- list()
sentinel[["kris"]] <- read_sf("~/Desktop/glaciers/data/labels/sentinel_kris/labels_kris.shp") %>%
  mutate(GL_ID = str_extract(file, "[:alnum:]+"))
sentinel[["sarah"]] <- read_sf("~/Desktop/glaciers/data/labels/sentinel/sentinel_labels.shp") %>%
  mutate(GL_ID = str_extract(file, "[:alnum:]+"))
bind_rows(sentinel) %>%
  write_sf("~/Desktop/glaciers/data/labels/sentinel_combined.shp")
```


```{r}
bing <- list()
bing[["sarah"]] <- read_sf("~/Desktop/glaciers/data/labels/bing/bing_labels.shp") %>%
  mutate(GL_ID = str_extract(file, "[:alnum:]+"))
bing[["kris"]] <- read_sf("~/Desktop/glaciers/data/labels/bing_kris.shp") %>%
  mutate(GL_ID = str_extract(file, "[:alnum:]+"))
bind_rows(bing) %>%
  write_sf("~/Desktop/glaciers/data/labels/bing_combined.shp")
```

```
scp sentinel_combined* azure://datadrive/snake/lakes/labeling/sentinel/
scp bing_combined* azure://datadrive/snake/lakes/labeling/bing/
```

Here is a script to split the "recent" file csv's according to the train / test
/ val split. The inputs are (1) the current split csv file, which includes all
the labeled glacier IDs / filenames but not whether they were a part of the
source basin (or moreover, whether they were trained on), (2) a train test split
file, a file specifying whether certain glacial lake IDs were present during
training of the original model (regardless of whether the imagery are the same
and despite the fact that the labels will have changed).

```{r}
library(readr)
library(dplyr)

recent_ids <- read_csv("../data/eval_paths/sentinel-unet_recent.csv")
splits <- read_csv("../data/sentinel_split_ids.csv") %>%
  mutate(sample_id = str_replace(`0`, ".tif", ""))
```

```{r}
library(tidyr)

join_data <- function(recent_ids, splits) {
  recent_ids %>%
    left_join(splits) %>%
    mutate(split = replace_na(split, "new")) %>%
    split(.$split)
}
```

```{r}
library(purrr)
recent_paths <- list.files("../data/eval_paths/", full = TRUE)
recent_ids <- map(recent_paths, ~ read_csv(.))
names(recent_ids) <- basename(recent_paths)

split_paths <- list.files("../data/", "*id", full = TRUE)
splits <- map(split_paths, ~ read_csv(.)) %>%
  map(~ mutate(., sample_id = str_replace(file, ".tif", "")))
names(splits) <- basename(split_paths)

for (path in names(recent_ids)) {
  if(str_detect(path, "bing")) {
    split_ <- splits[["bing_split_ids.csv"]]
  } else {
    split_ <- splits[["sentinel_split_ids.csv"]]
  }
    
  result <- join_data(recent_ids[[path]], split_)
  for (split_str in names(result)) {
    result[[split_str]] %>%
      select(path, sample_id) %>%
      write_csv(str_replace(path, "recent", str_c("recent", "_", split_str)))
  }
}

#split_paths(recent_ids, splits)
```


